Within chert: a multi-technique mineral and geochemical approach to the study of chert of southwestern Iberia

### 2025-05-03 analysis/paper/paper.qmd
Small updates + ggsaves for the main thesis

@@

plot_grid(sp58_plot, sp69_plot, labels = c("a", "b"), nrow = 2)

@@

@@

```{r}
#| label: fig-pxrf-boxplots
#| fig-cap: "Boxplots of raw element percentages (a: SiO2, b: CaO, c: Fe2O3, d: TiO2) by geological formation or archaeological chert type. Only chert groups with n>5 were included in the boxplots."
#| fig-width: 7
#| fig-height: 7
#| fig-align: center

ggarrange(si_boxplot, ca_boxplot, fe_boxplot, ti_boxplot, labels = c("a","b","c","d"), ncol = 2, nrow = 2, common.legend = TRUE, legend = "bottom")

@@

plot_grid(biplot_alg, biplot_nl, biplot_comp, biplot_comp2, labels = c("a", "b", "c", "d"))

>>>>

#ggsave("xrd_15.png", bg = "white", width = 7, height = 5, unit ="in", dpi = 300, path = "analysis")

@@

grid_plot <- plot_grid(sp58_plot, sp69_plot, labels = c("a", "b"), nrow = 2)

#ggsave("grid_plot.png", bg = "white", width = 7, height = 8, unit ="in", dpi = 300, path = "analysis")

@@

#ggsave("succ_barplot.png", bg = "white", width = 6, height = 4, unit ="in", dpi = 300, path = "analysis")

@@

```{r}
#| label: fig-pxrf-boxplots
#| fig-cap: "Boxplots of raw element percentages (a: SiO2, b: CaO, c: Fe2O3, d: TiO2) by geological formation or archaeological chert type. Only chert groups with n>5 were included in the boxplots. Diamond symbol represents mean values within each group."
#| fig-width: 7
#| fig-height: 7
#| fig-align: center

pxrf_boxplots <- ggarrange(si_boxplot, ca_boxplot, fe_boxplot, ti_boxplot, labels = c("a","b","c","d"), ncol = 2, nrow = 2, common.legend = TRUE, legend = "bottom")

#ggsave("pxrf_boxplots.png", bg = "white", width = 7, height = 7, unit ="in", dpi = 300, path = "analysis")

@@

pca_plots <- plot_grid(biplot_alg, biplot_nl, biplot_comp, biplot_comp2, labels = c("a", "b", "c", "d"))

#ggsave("pca_plots.png", bg = "white", width = 9, height = 7, unit ="in", dpi = 300, path = "analysis")
